\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[nonumberlist, toc, nogroupskip, nopostdot, style=altlist]{glossaries}

\newcommand{\longglos}{\longnewglossaryentry}

\makeglossaries

\newglossaryentry{latex}
{
  name=latex,
  description={Is a mark up language specially suited for scientific documents}
}

\newglossaryentry{maths}
{
  name=mathematics,
  description={Mathematics is what mathematicians do}
}

\newglossaryentry{formula}
{
  name=formula,
  description={A mathematical expression}
}

\longnewglossaryentry{at random}
{name={at random}}
{%
    Without a governing design, method, or purpose; unsystematically:\\
    Chose a card at random from the desk.
}

\longnewglossaryentry{consequence}
{name={consequence}}
{%
  the effect, result, or outcome of something occurring earlier:\\
  The accident was the consequence of reckless driving.
}

\longnewglossaryentry{pertain}
{name={pertain}}
{%
  Be appropriate, related, or applicable to.\\
  The university relations officer works to represent students on all matters pertaining to governance of the university.\\
  My father was very sure about certain matters pertaining to the universe.
}

\longnewglossaryentry{facilitate}
{name={facilitate}}
{%
  to make something possible or easier:\\
  The new ramp will facilitate the entry of wheelchairs.\\
  The current structure does not facilitate efficent work flow.
}

\longnewglossaryentry{interdisciplinary}
{name={interdisciplinary}}
{%
  combining or involving two or more academic disciplines or fields of study:\\
  The economics and history departments are offering an interdisciplinary seminar on Asia.
}

\longnewglossaryentry{subsequent}
{name={subsequent}}
{%
  coming after something in time; following:\\
  occurring or coming later or after (often followed by to): subsequent events:\\
  The theory was developed subsequent to the earthquake of 1906.\\
  Subsequent to their arrival in Chicago, they bought a new car.\\
  following in order or succession; succeeding:\\
  a subsequent section in a treaty.
}

\longnewglossaryentry{succession}
{name={succession}}
{%
  a number of people or things of a similar kind following one after the other:\\
  She had been secretary to a succession of board directors.
}

\longnewglossaryentry{secretary}
{name={secretary}}
{%
  someone who works in an office, writing letters, making phone calls, and arranging meetings for a person or for a organization:\\
  Unless it's marked 'private', my secretary usually opens my post.
}

\longnewglossaryentry{BofD}
{name={Board of Directors}}
{%
  A board of directors governs a corporation. It is a group of people who are elected by a company's shareholders to meet periodicaly to oversee thecompany's management and represent the interests of the shareholders.\\
  The board of directors may be comprised of senior managers of the company, as well as outsiders with special skills that can be of assistance to the company.
}

\longnewglossaryentry{celestial}
{name={celestial}}
{%
  positioned in or relating to the sky, or outer space as observed in astronomy:\\
  A celestial body.\\
  Galileo took the position that all celestial phenomena should be interpreted in terms of terrestrial analogies, against Aristotle's basic postulate of essential differences.
}

\longnewglossaryentry{interpret}
{name={interpret}}
{%
  Explain the meaning of (information or actions):\\
  The evidence is difficult to interpret.
}

\longnewglossaryentry{terrestrial}
{name={terrestrial}}
{%
  On or relating to the earth:\\
  Increased  ultraviolet radiation may disrupt terrestrial ecosystems.
}

\longnewglossaryentry{aperiodic}
{name={aperiodic}}
{%
  not periodic; irregular:
}

\longnewglossaryentry{autonomous}
{name={autonomous}}
{%
  (of a country or region) having the freedom to govern itself or control its own affairs.\\
  The federation included sixteen autonomous republics.
}

\longnewglossaryentry{republic}
{name={republic}}
{%
  A state in which supreme power is held by the people and their elected representatives, and which has an elected or nominated president rather than a monarch.
}

\longnewglossaryentry{federation}
{name={federation}}
{%
  A group of states with a central governemnt but independence in internal affairs.\\
  {[in names]} 'the Russian Federation'\\
  To be sure, as the history of the European Union shows, there can be federalism without a federation.
}

\longnewglossaryentry{AKA}
{name={Also Known As}}
{%
  AKA means "Also Known As." AKA is an acronym, abbreviation or slang word that is explained above where the AKA definition is given.
}

\longnewglossaryentry{burn_candle}
{name={burn the candle at both ends}}
{%
  to work very hard and stay up very late at night. (One end of the candle is work done in the daylight, and the other end is work done at night.):\\
  to regularly stay awake late and get up early because you are too busy.:\\
  No wonder Mary is ill. She has been burning the candle at both ends for a long time.
}

\longnewglossaryentry{inspect}
{name={inspect}}
{%
  to look carefully at or over; view closely and critically:\\
  to view or examine formally or officially:\\
  examine, scrutinize, investigate, study:\\
  Take time to read the small print on the packages you inspect at the market.
}

\longnewglossaryentry{strive}
{name={strive}}
{%
  to exert oneself vigorously; try hard:\\
  to make strenuous efforts toward any goal:\\
  He strove to make himself understood.
}

\longnewglossaryentry{ingenuity}
{name={ingenuity}}
{%
  the quality of being cleverly inventive or resourceful; inventiveness:\\
  cleverness or skillfullness of conception or design:\\
  Our economy is stronger when we harness the talents and ingenuity of striving, hopeful immigrants.
}

\longglos{vital}
{name={vital}}
{%
  absolutely necessary; essential:\\
  full of energy; lively:\\
  Secrecy is of vital importance.\\
  "A beautiful, vital girl"
}

\longglos{secrecy}
{name={secrecy}}
{%
  the action of keeping something secret or the state of being kept secret:\\
  The bidding is conducted in secrecy.\\
  "A meeting held in secrecy"
}

\longglos{watershed}
{name={watershed}}
{%
  an area or ridge of land that separates waters flowing to different rivers, basins, or seas:\\
  an event or period making a turning point in a situation:\\
  These works were a watershed in the history of music.
}

\longglos{insight}
{name={insight}}
{%
  the capacity to gain an accurate and deep understanding of someone or something:\\
  an accurate and deep understanding:\\
  His work provides important insights into language use.
}

\longglos{equilibrium}
{name={equilibrium}}
{%
  a state in which opposing forces or influences are balanced:\\
  a state of physical balance:\\
  a calm state of mind:\\
  The task is the maintenance of social equilibrium.\\
  I stumbled over a rock and recovered my equilibrium.
}

\longglos{inherent}
{name={inherent}}
{%
  Existing in something as a permanent, essential, or characteristic attribute:
  The authors point out that this vulnerability is an inherent part of the existing system.
}

\longglos{grail}
{name={grail}}
{%
  (usually initial capital letter). Also called Holy Grail. a cup or chalice that in medieval legend was associated with unusual powers, especially the regeneration of life and, later, Christian purity, and was much sought after by medieval knights: identified with the cup used at the Last Supper and given to Joseph of Arimathea.\\
  (sometimes initial capital letter) Informal. any greatly desired and sought-after objective; ultimate ideal or reward.
}

\longglos{adhere}
{name={adhere}}
{%
  to stay attached; stick fast; cleave; cling:
  Physics. (of two or more dissimilar substances) to be united by a molecular force acting in the area of contact.
  The mud adhered to his shoes.
}

\longglos{ascend}
{name={ascend}}
{%
  go up or climb. moving upward.\\
  She ascended the stairs.
}

\title{How to create a glossary}
\author{Shota Tsuji}
\date{\today}

\begin{document}
\maketitle
\newpage

\tableofcontents
\clearpage

\section{First Section}
The \Gls{latex} typesetting markup language is specially suitable
for documents that include \gls{maths}.

\clearpage

%\glsaddall[types=symbolslist]
\glsaddall
\printglossary

\end{document}
